% !TeX root = main.tex
% !TEX program = xelatex

\documentclass[]{rahulworld-resume}
\usepackage{hyperref}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}
    \begin{large}
        \headername{Jamer José Rebolledo Quiroz}
        \\
    \end{large}

    \textsc{Backend Developer.}\\
    \textsc{Full Stack Web Developer.}


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     LINKS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Links}
    \noindent\rule{5cm}{0.4pt}

    Github: \href{https://github.com/jamerrq}{\custombold{jamerrq}} \\
    LinkedIn: \href{https://www.linkedin.com/in/jamerrq}{\custombold{jamerrq}} \\
    Portfolio: \href{https://my-portfolio-jamerrq.netlify.app/}{\custombold{My
            Portfolio}}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Skills}
    \noindent\rule{5cm}{0.4pt}
    \subsection{Languages}
    Spanish (Native)\\
    English (B2) EF SET 58/100\footnote{https://www.efset.org/cert/qS2qV4}\\
    \vspace{1pt}
    \subsection{operating systems}
    GNU/Linux\\
    \vspace{1pt}
    \subsection{Programming Languages}
    Python, JavaScript,\\
    Typescript, Bash, Haskell\\
    \vspace{1pt}
    \subsection{Databases}
    SQL: PostgreSQL\\
    NoSQL: MongoDB\\
    \vspace{1pt}
    \subsection{Backend}
    Node.js, C\# .NET, ExpressJS\\
    \subsection{Frontend}
    React, Redux, NextJS, \\
    Astro, Vite, Tailwind CSS\\

    \sectionsep
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     COURSEWORK
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Coursework}
    \noindent\rule{5cm}{0.4pt}

    Data Structures and Algorithms\\
    Databases\\
    Machine Learning\\
    Heuristic Optimization\\
    \sectionsep
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Education}
    \noindent\rule{3cm}{0.4pt}\\
    \datecolor{2017-2022}
    \subsection{B.Tech. in \\
        Mathematical Engineering} EAFIT University \\
    GPA : 3.84/5\\

    \subsection{Full Stack Web Development}
    Academia Henry

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN TWO
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}
    % \descript{BS in Computer ence}
    \hspace*{0pt}\hfill    \\
    \hspace*{0pt}\hfill    \\
    \hspace*{0pt}\hfill Medellin, Colombia\\
    \hspace*{0pt}\hfill Mob.: +57-3008163841 \\
    \hspace*{0pt}\hfill Email:
    \textit{\href{mailto:janerrq@gmail.com}{jamerrq@gmail.com}}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Experience in Industry}
    \noindent\rule{12.5cm}{0.4pt} \customit{3+ years of experience as a software developer.}\\
    \noindent\rule{12.5cm}{0.4pt}

    \datecolor{\ \ \ \ \ \ \ 2023+}\runsubsection{\custombold{Dium}}
    \descript{\custombold{Backend Developer}}
    \noindent
    \hspace{5em}%
    \begin{minipage}{0.85\textwidth\vspace{2pt}} Responsible for the development of
        the backend (testing, CI and building to production) of the web app, the implementation of the REST API, and the
        integration with the frontend. The technologies used are Node.js, Express.js,
        and PostgreSQL with Sequelize.
    \end{minipage}

    \datecolor{\ \ \ \ \ \ \ \ \ 2022}\runsubsection{\custombold{Comfama - Universidad EAFIT}}
    \descript{\custombold{Teaching assistant}}
    \noindent
    \hspace{5em}%
    \begin{minipage}{0.85\textwidth\vspace{2pt}} Responsible for the preparation of
        the course material, the development of the course, the evaluation of the
        students, and giving lectures about the introduction to programming, data
        structures and algorithms, and artificial intelligence applied to real life
        problems.

    \end{minipage}

    \datecolor{2020-2021}\runsubsection{\custombold{Bancolombia Personas}}
    \descript{\custombold{Data Scientist}}
    \noindent
    \hspace{5em}%
    \begin{minipage}{0.85\textwidth\vspace{2pt}} Responsible of the development of
        daily reports, analysis of the data, and the implementation of machine learning
        models to predict the behavior of products and services of the company.
    \end{minipage}
    \sectionsep


    \datecolor{2019-2023}\runsubsection{\custombold{Freelance Software Developer}}
    \descript{\custombold{Software Developer}}
    \noindent
    \hspace{5em}%
    \begin{minipage}{0.85\textwidth\vspace{2pt}} I have been working as a
        consultant, teacher assistant, researcher and software developer for several
        departments of my university. The projects that I have been working on are
        related to courses such as optimization, statistics, operations
        research, web development, and data science.
    \end{minipage}
    \noindent\rule{12.5cm}{0.4pt}
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SIDE PROJECT
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % \section{Scientific Presentations and Articles}

    % \noindent
    % \begin{itemize}
    %     %\item Rebolledo,  Q.; Rivera,  J.; A note on ``Scheduling the South
    %     %American Qualifiers to the 2018 FIFA World Cup by integer programming''.
    %     \item Rebolledo, Q., Rivera, J. 2019-2021. \textit{Scheduling of Colombian
    %               professional soccer league: A comparison of models}.
    %           \href{https://github.com/jamerrq/20192-Sport-Scheduling}{\custombold{Repository}}.
    % \end{itemize}



    \section{Projects}

    \begin{itemize}
        \item
              \href{https://github.com/Ide-Pinturerias/pinturas-app-back}{\custombold{Backend
                      server for IDE Pinturerías.}} It allows the management of products, clients,
              orders, while also providing a REST API for the frontend to consume. This
              project was made using Node.js, Express.js, and PostgreSQL with Sequelize.

        \item
              \href{https://pinturas-app-front.vercel.app/}
              {\custombold{Frontend UI for IDE Pinturerías.}} It holds the user
              interface for the management of products, clients, orders, and
              the authentication of the users. This project was made using
              React, Redux, Vite and Tailwind CSS.



        \item \href{https://resources-app.vercel.app/}{\custombold{Resources
                      App.}} A collection of resources for web full stack development. Built with
              Next.js, Typescript and Tailwind CSS.

        \item More projects
              \href{https://jamerrq-com.vercel.app/projects}{\custombold{here}}

    \end{itemize}

    \section{Awards / Honors}

    \begin{itemize}
        \item \custombold{2017-2022}: Government scholarship granted by the
              Colombian Ministry of Education to the best students in the national exams.
              % \item \custombold{2020}: Assisted to the first Facebook Hackathon in
              %       Colombia, with a performance of 4th place among more than 100 participants.
    \end{itemize}
\end{minipage}


\end{document}
